---
title: "Estimate trophic position - one source model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate trophic position - one source model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
  knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```

## Our Objectives

The purpose of this vignette is to learn how to estimate trophic position of a 
species using stable isotope data
($\delta^{13}C$ and $\delta^{15}N$). We can estimate trophic position using 
a one source model based on equations from 
[Post 2002](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2).

## Trophic Position Model

For a one source model from [Post 2002](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2)
the equation consists of the following: 



$$
\text{Trophic Position} = \lambda + \frac{(\delta^{15}N_c - \delta^{15}N_b)}{\Delta N}
$$



Where $\lambda$ is the trophic position of the baseline (e.g., `2`), 
$\delta^{15}N_c$ is the $\delta^{15}N$ of the consumer, $\delta^{15}N_b$ is the 
$\delta^{15}N$ of the baseline, and $\Delta N$ is the trophic enrichment factor 
(e.g., 3.4). 

To use this model with a Bayesian framework, we need to rearrange 
this equation. A function in {trps}, `one_source_model()` 
uses this rearranged equation below: 


$$
\delta^{15}N_c = \delta^{15}N_b + \Delta N \times (\text{Trophic Position} - \lambda)  
$$


## Vignette structure   

First we will need to organize the data prior to running the model. 
To do this work we will use [{dplyr}](https://dplyr.tidyverse.org/) and 
[{tidyr}](https://tidyr.tidyverse.org/) but we could also use 
[{data.table}](https://rdatatable.gitlab.io/data.table/) to do this work. 

When running the model we will use [{trps}](https://benjaminhlina.github.io/trps/) 
and [{brms}](https://paulbuerkner.com/brms/) and iterative processes provided 
by [{purrr}](https://purrr.tidyverse.org/). 

Once we have run the model we will use [{bayesplot}](https://mc-stan.org/bayesplot/) 
to assess models and then extract posterior draws using 
[{bayestestR}](https://easystats.github.io/bayestestR/) and 
[{tidybayes}](http://mjskay.github.io/tidybayes/). 
Posterior distributions will be plotted using [{ggplot2}](https://ggplot2.tidyverse.org/) 
and [{ggdist}](https://mjskay.github.io/ggdist/).

## Load packages 

Below we will load all the packages needed to carry out the analysis.

```{r setup, message=FALSE}
{
  library(bayesplot)
  library(bayestestR)
  library(brms)
  library(dplyr)
  library(ggplot2)
  library(ggdist)
  library(purrr)
  library(tidybayes)
  library(tidyr)
  library(trps)
}
```

## Assess data 

In [{trps}](https://benjaminhlina.github.io/trps/) we have several data sets, 
they include stable isotope data ($\delta^{13}C$ and $\delta^{15}N$) for a
consumer, lake trout (*Salvelinus namaycush*), a benthic baseline, amphipods, 
and a pelagic baseline, dreissenids for a ecoregion in Lake Ontario. 

### Consumer data

We will check out each data set with the first being the consumer. 
```{r}
consumer_iso
```

We can see that this data set contains the common name of the consumer 
(`common_name`), the ecoregion samples were collected (`ecoregion`) and 
$\delta^{13}C$ (`d13c`) and and $\delta^{15}N$ (`d15n`). 

### Baseline data 

Next for this vignette we will only assess and use benthic baseline data set.

```{r}
baseline_1_iso
```

We can see that this data set contains the common name of the baseline 
(`common_name`), the ecoregion samples were collected (`ecoregion`) and 
$\delta^{13}C$ (`d13c`) and and $\delta^{15}N$ (`d15n`). 

## Organizing data 

Now that we understand the data we need to combine both data sets to estimate 
trophic position for our consumer. To do this we first need to make an `id` 
column in each data set that will assist in joining them together.  We will
first `arrange()` the data by `ecoregion` and then `common_name`. We will then 
`group_by()` the same variables and add `id` for each grouping using 
`row_number()`. Always `ungroup()` the data frame after completing 
`group_by()`. Lastly, we will use `dplyr::select()` rearrange the order of the 
columns. 

### Consumer data

Let's first add `id` to `consumer_iso` data frame.  

```{r}
consumer_iso <- consumer_iso %>% 
  arrange(ecoregion, common_name) %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, common_name:d15n)
```

### Baseline data 

Next let's add `id` to  `baseline_1_iso` data frame. For joining purposes we 
are going to drop `common_name` from this data frame. 

```{r}
baseline_1_iso <- baseline_1_iso %>% 
  arrange(ecoregion, common_name) %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, ecoregion:n1)
```

### Joining isotope data 

Now that we have the consumer and baseline data sets in a consistent
structure we can join them by `"id"` and `"ecoregion"`
using `left_join()` from {dplyr}. We will also add in 
the constant $\lambda$ (`l1`) to our data frame. 

```{r}
combined_iso_os <- consumer_iso %>% 
  left_join(baseline_1_iso, by = c("id", "ecoregion")) %>% 
  mutate(
    l1 = 2
  )
```

We can see that we have successfully combined our consumer and baseline data.

```{r}
combined_iso_os
```

Important note, to run the model successfully columns need to be names `d15n`, 
`n1`, and `l1`. 

## Bayesian Analysis

We can now estimate trophic position for lake trout in an ecoregion of
Lake Ontario. 

There are a few things to know about running a Bayesian analysis, I suggest 
reading these resources:

### Priors 

Bayesian analyses rely on supplying uninformed or informed prior distributions 
for each parameter (coefficient; predictor) in the model. The default informed
priors for a one source model are the following, $\Delta N$ assumes a normal 
distribution (`dn`; $\mu = 3.4$; 
$\sigma = 0.25$), trophic position assumes a uniform distribution 
(lower bound = `2`and upper bound = `10`), $\sigma$ assumes a uniform 
distribution (lower bound = `0` and upper bound = `10`) and if 
informed priors are desired for $\delta^{15}N_b$ (`n1`; $\mu = 9$; 
$\sigma = 1$), we can set the argument `bp` to `TRUE` in 
all `one_source_` functions. 

### Model convergence 
Some important things to pay attention to are 
always run at least 2 chains, if the model does not converge you can try 
to increase the amount of samples that are burned-in (discarded; in brms 
this can be controlled by the argument `warmup`), increase the number of 
iterative samples retained (in `brm()` this can be controlled by the 
argument `iter`), and/or adjust the `adapt_delta` value using 
`control = list(adapt_delta = 0.95)`. 

When assessing the model we want R-hat to be 1 or within 0.05 of 1, we also want 
a high value for effective sample size (ESS), we want trace plots to look 
"grassy" or "catapillery", and we want posterior distributions to look relatively
normal. 

## Estimating trophic position 

We will use functions from {trps} that drop into a {brms} model. These 
functions are `one_source_model()` which provides `brm()` the formula structure
needed to run a one source model. Next `brm()` needs the structure of the 
priors which can be supplied to the `prior` argument using `one_source_priors()`. 
Lastly, values for these priors are supplied through the `stanvars` argument 
using `one_source_priors_params()`. You can adjust the mean ($\mu$),  
variance ($\sigma$), or upper and lower bounds (`lb` and `ub`) for each prior 
of the model within `one_soruce_priors_params()`, however, only adjust priors 
if you have a good grasp of Bayesian frameworks and your study system and 
species. 

### Model 
Let's run the model! 

```{r}
m <- brm(
  formula = one_source_model(),
  prior = one_source_priors(),
  stanvars = one_source_priors_params(),
  data = combined_iso_os,
  family = gaussian(),
  chains = 2,
  iter = 4000,
  warmup = 1000,
  cores = 4,
  seed = 4,
  control = list(adapt_delta = 0.95)
)
```

### Model output 

Let's view the summary of the model. 

```{r}
m
```
We can see that the R-hat is 1 meaning that variance among and within chains is 
equal (See [{rstan} docmentation on R-hat](https://mc-stan.org/rstan/reference/Rhat.html)).
and that ESS is quite large. Overall, this means the model is converging 
and fitting accordingly. 

### Trace plots 
Let's view trace plots and posterior distributions for the model. 

```{r}
plot(m)
```

We can see that the trace plots look "grassy" meaning the model is converging!  

## Posterior draws 

Let's again look at the summary output from the model. 

```{r}
m
```

We can see that $\Delta N$ is estimated to be `3.38` with  `l-95% CI` of `2.90`, 
and `u-95% CI` of `3.87`. If we move down to trophic position (`tp`) we 
see trophic position is estimated to be `4.41` with `l-95% CI` of `3.97`, 
and `u-95% CI` of `4.92`. 

### Extract posterior draws 

We will use functions from {tidybayes} to do this work. First we will look at 
the the names of the variables we want to extract using `get_variables()`. 

```{r}
get_variables(m)
```

You will notice that `"b_tp_Intercept"` is the name of the variable in the 
model object that we are most interested in extracting. We then get posterior 
draws using `gather_draws()`. I am going to rename `"b_tp_Intercept"` to `tp`. 

```{r}
post_draws <- m %>% 
  gather_draws(b_tp_Intercept) %>% 
  mutate(
    .variable = "tp"
  )
```

Let's view the `post_draws`

```{r}
post_draws
```
We can see that this consists of five variables `.chain`, `.itteration`, 
`.draw`, `.variable` (this will have different variables of interest if you 
supply `gather_draws()` with more than one variable), `.value` (estimated value). 

## Ploting posterior distributions  

Now that we have our posterior draws extracted we can plot them. For comparing 
trophic position among species or groups, I like using either 
violin plots, interval points, or slab plots for posteriors. We can access 
violins through {ggplot2} with the later being available in {ggdist}. 

For this example, however, we are going to plot the density for posterior
draws using `geom_desnity()`. I'll demonstrate below how to run the model 
with an iterative process to produce estimates of trophic position for more 
than one group (e.g., comparing trophic position among species or different 
ecoergion). 


```{r}
ggplot(data = post_draws, aes(x = .value)) + 
  geom_density() + 
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank()
  ) + 
  labs(
    x = "P(Trophic Position | X)", 
    y = "Density"
  )
```

Congratulations we have estimate trophic position for Lake Trout! We will 
further compare trophic position for Lake Trout among different regions 
below with some data already formatted and ready to go that is in the package. 

## Estimate trophic position - multiple groups 

In {trps} we have a data set that has consumer and baseline data already joined 
for two ecoregions (`combined_iso`). Let's look at this data frame. 

### Organize data - multiple groups 
```{r}
combined_iso
```

We can see that this data frame has a isotope data for a 
second baseline (dreissenids; `c2` and `n2`) as well as the mean values for both 
baselines. These columns will be used when estimating trophic position 
using a two source model and will need to be removed these columns. We can 
also confirm that this data set has one species, lake trout, collected from 
two ecoregions in Lake Ontario. 

```{r}
unique(combined_iso$ecoregion)
```

Let's remove the columns we don't need, `c2`, `n2`, `c1_mean`, `n1_mean`, 
`c2_mean`, `n2_mean`. We also need to add $\lambda$ to the data frame (`l1`), 
and I am going to make a `name` column that will be the two groups we have 
`common_name` and `ecoregion` pasted together. We are doing this to make the 
itterative processes easier. 

```{r}
combined_iso_update <- combined_iso %>% 
  dplyr::select(-c(c2:n2_mean)) %>% 
  mutate(
    l1 = 2, 
    name = paste(ecoregion, common_name, sep = "_")
  )

combined_iso_update
```

This example data is now ready to be analyzed. 

## Model trophic position - multiple groups 

We will use similar structure as before to model however, we will first `split()` 
the data into a list for all group combinations and then use `map()` from 
{purrr} to run the model for each group.

You will notice that the `brm()` call is exactly the same as when we ran the model
for one group. The only difference here is we are using `map()` and replacing the 
`data` argument in `brm()` with `.x` to tell `brm()` and `map()` where to get 
the data.

### Model - multiple groups 
Let's run the model! 

```{r}
m1 <- combined_iso_update %>% 
  split(.$name) %>% 
  map( ~ brm(
    formula = one_source_model(),
    prior = one_source_priors(),
    stanvars = one_source_priors_params(),
    data = .x,
    family = gaussian(),
    chains = 2,
    iter = 4000,
    warmup = 1000,
    cores = 4,
    seed = 4,
    control = list(adapt_delta = 0.95)
  ), 
  .progress = TRUE
  )
```

### Model output - multiple groups 
Let's look at the summary of both models. 

```{r}
m1
```

We can see that the R-hat is 1 meaning that variance among and within chains is 
equal (See [{rstan} docmentation on R-hat](https://mc-stan.org/rstan/reference/Rhat.html)).
and that ESS is quite large. Overall this means the both models are converging 
and fitting accordingly. 

### Trace plots  
Let's look at the trace plots and distributions. We will use `walk()` instead 
of `map()` here as `walk()` invisibly return .x which is handy when you want to c
all a function (`plot()`) for its side effects rather than its return value.

```{r}

m1 %>% 
  iwalk(~ {
    plot(.x) 
    grid::grid.text(.y, x = 0.5, y = 0.98)
  })
```

We can see that the trace plots look "grassy" meaning the model is converging!  

## Posterior draws - multiple groups 

Let's again look at the summary output from the model. 

```{r}
m1
```

We can see for lake trout from the Anthropogenic ecoregion that
$\Delta N$ is estimated to be `3.39` with  `l-95% CI` of `2.91`, 
and `u-95% CI` of `3.86`. If we move down to trophic position (`tp`) we 
see trophic position is estimated to be `4.48` with `l-95% CI` of `4.43`, 
and `u-95% CI` of `5.39`. 

We can see for lake trout from the Ebayment ecoregion that 
$\Delta N$ is estimated to be `3.38` with  `l-95% CI` of `2.90`, 
and `u-95% CI` of `3.87`. If we move down to trophic position (`tp`) we 
see trophic position is estimated to be `4.41` with `l-95% CI` of `3.97`, 
and `u-95% CI` of `4.92`. 

### Extract posterior draws - multiple groups  


We will use functions from {tidybayes} to do this work. First we will look at 
the the names of the variables we want to extract using `get_variables()`. 
Considering we have multiple models in `m1` we need to use `map()` to iterate
over `m1`. 

```{r}
m1 %>% 
  map(~ get_variables(.x))
```

You will notice that `"b_tp_Intercept"` is the name of the variable in the 
model object that we are most interested in extracting. We then get posterior 
draws using `gather_draws()`.  I am going to rename `"b_tp_Intercept"` to `tp`. 

```{r}
post_draws_mg <- m1 %>%
  map(~ .x %>% 
  gather_draws(b_tp_Intercept) %>% 
  mutate(
    .variable = "tp"
  )
  ) %>% 
  bind_rows(.id = "name") %>% 
  separate_wider_delim(name, names = c("ecoregion", "common_name"), 
                              delim = "_") %>% 
  mutate(
    ecoregion = factor(ecoregion, 
                       levels = c("Anthropogenic", "Embayment")), 
  )
```

Let's view the `post_draws`

```{r}
post_draws_mg
```
We can see that this consists of seven variables, `ecoregion`, `common_name`,
`.chain`, `.itteration`, `.draw`, `.variable` 
(this will have different variables of interest if you 
supply `gather_draws()` with more than one variable), `.value` (estimated value). 

Note - the first two columns will vary depending on the names you split your data
up into. 

## Ploting posterior distributions - multiple groups  

Now that we have our posterior draws extracted we can plot them. For comparing 
trophic position among species or groups, I like using either 
violin plots, interval points, or slab plots for posteriors. We can access 
violins through {ggplot2} with the later being available in {ggdist}. 

```{r}
ggplot(data = post_draws_mg, aes(x = common_name, 
                                 y = .value, 
                                 fill = ecoregion)) + 
  geom_violin() + 
  stat_summary(fun = median, geom = "point", 
               size = 3, 
               position = position_dodge(0.9)
               ) + 
  scale_fill_viridis_d(name = "Ecoregion", 
                       option = "G", 
                       begin = 0.35, 
                       end = 0.75, alpha = 0.65) + 
  theme_bw(base_size = 15) + 
  theme(
    panel.grid = element_blank(),
    legend.position = "inside", 
    legend.position.inside = c(0.85,  0.86)
  ) +
  labs(
    x = "Species", 
    y = "P(Trophic Position | X)"
  )
```


Congratulations we have successfully run a Bayesian one source trophic position 
model for one species in two ecoregions of Lake Ontario! 
