---
title: "Estimate trophic position - one source model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate trophic position - one source model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

## Our Objectives

The purpose of this vignette is to learn how to estimate trophic position of a 
species using stable isotope data
($\delta^{13}C$ and $\delta^{15}N$). We can estimate trophic position using 
a one source model based on equations from 
[Post 2002](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2).

## Trophic Position Model

For a one source model from [Post 2002](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2)
the equation consists of the following: 



$$
\text{Trophic Position} = \lambda + \frac{(\delta^{15}N_c - \delta^{15}N_b)}{\Delta N}
$$



Where $\lambda$ is the trophic position of the baseline (e.g., `2`), 
$\delta^{15}N_c$ is the $\delta^{15}N$ of the consumer, $\delta^{15}N_b$ is the 
mean $\delta^{15}N$ of the baseline, and $\Delta N$ is the trophic enrichment factor 
(e.g., 3.4). 

To use this model with a Bayesian framework, we need to rearrange 
this equation. A function in [{trps}](https://benjaminhlina.github.io/trps/) , `one_source_model()`, uses this rearranged equation below: 


$$
\delta^{15}N_c = \delta^{15}N_b + \Delta N \times (\text{Trophic Position} - \lambda) 
$$


## Vignette structure  

First we will need to organize the data prior to running the model. 
To do this work we will use [{dplyr}](https://dplyr.tidyverse.org/) and 
[{tidyr}](https://tidyr.tidyverse.org/) but we could also use 
[{data.table}](https://rdatatable.gitlab.io/data.table/). 

When running the model we will use [{trps}](https://benjaminhlina.github.io/trps/) 
and [{brms}](https://paulbuerkner.com/brms/) and iterative processes provided 
by [{purrr}](https://purrr.tidyverse.org/). 

Once we have run the model we will use [{bayesplot}](https://mc-stan.org/bayesplot/) 
to assess models and then extract posterior draws using 
[{tidybayes}](http://mjskay.github.io/tidybayes/). 
Posterior distributions will be plotted using [{ggplot2}](https://ggplot2.tidyverse.org/)
and [{ggdist}](https://mjskay.github.io/ggdist/) with colours provided by 
[{viridis}](https://sjmgarnier.github.io/viridis/).

## Load packages 

Below we will load all the packages needed to carry out the analysis.

```{r setup, message=FALSE}
{
library(bayesplot)
library(brms)
library(dplyr)
library(ggplot2)
library(ggdist)
library(grid)
library(purrr)
library(tidybayes)
library(tidyr)
library(trps)
library(viridis)
}
```

## Assess data 

In [{trps}](https://benjaminhlina.github.io/trps/) we have several data sets, 
they include stable isotope data ($\delta^{13}C$ and $\delta^{15}N$) for a
consumer, lake trout (*Salvelinus namaycush*), a benthic baseline, amphipods, 
and a pelagic baseline, dreissenids, for an ecoregion in Lake Ontario. 

### Consumer data

We will check out each data set with the first being the consumer. 
```{r}
consumer_iso
```

We can see that this data set contains the `common_name` of the consumer 
, the `ecoregion` samples were collected from, and 
$\delta^{13}C$ (`d13c`) and $\delta^{15}N$ (`d15n`). 

### Baseline data 

Next for this vignette we will only assess and use the benthic baseline data set.

```{r}
baseline_1_iso
```

We can see that this data set contains the `common_name` of the baseline, the `ecoregion` samples were collected from, and 
$\delta^{13}C$ (`d13c_b1`) and $\delta^{15}N$ (`d15n_b1`). 

## Organizing data 

Now that we understand the data we need to combine both data sets to estimate 
trophic position for our consumer. 

To do this we first need to make an `id` 
column in each data set that will assist in joining them together. We will
first `arrange()` the data by `ecoregion` and `common_name`. Next we will 
`group_by()` the same variables, and add `id` for each grouping using 
`row_number()`. Always `ungroup()` the `data.frame` after using 
`group_by()`. Lastly, we will use `dplyr::select()` to rearrange the order of the columns. 

### Consumer data

Let's first add `id` to `consumer_iso` data frame. 

```{r}
consumer_iso <- consumer_iso %>% 
  arrange(ecoregion, common_name) %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, common_name:d15n)
```

### Baseline data 

Next let's add `id` to `baseline_1_iso` data frame. For joining purposes we 
are going to drop `common_name` from this data frame. 

```{r}
baseline_1_iso <- baseline_1_iso %>% 
  arrange(ecoregion, common_name) %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, ecoregion:d15n_b1)
```

### Joining isotope data 

Now that we have the consumer and baseline data sets in a consistent
format we can join them by `"id"` and `"ecoregion"`
using `left_join()` from [{dplyr}](https://dplyr.tidyverse.org/).

```{r}
combined_iso_os <- consumer_iso %>% 
  left_join(baseline_1_iso, by = c("id", "ecoregion"))
```

We can see that we have successfully combined our consumer and baseline data. 
We need to do one last thing prior to analyzing the data and that is 
calculate the mean $\delta^{13}C$ (`c1`) and $\delta^{15}N$ (`n1`) for the 
baseline and add in the constant $\lambda$ (`l1`) to our data frame. 
We will do this by `groub_by()` our two groups, then using `mutate()` and `mean()` to calculate the mean values. 

Important note, to run the model successfully columns need to be named `d15n`, 
`n1`, and `l1`. 

```{r}
combined_iso_os <- combined_iso_os %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    c1 = mean(d13c_b1, na.rm = TRUE),
    n1 = mean(d15n_b1, na.rm = TRUE),
    l1 = 2
  ) %>% 
  ungroup()

combined_iso_os
```
and it is now ready to be analyzed!

## Bayesian Analysis

We can now estimate trophic position for lake trout in an ecoregion of
Lake Ontario. 

There are a few things to know about running a Bayesian analysis, I suggest 
reading these resources:

1. [Basics of Bayesian Statistics - Book](https://statswithr.github.io/book/)
2. [General Introduction to brms](https://www.jstatsoft.org/article/view/v080i01) 
3. [Estimating non-linear models with brms](https://paulbuerkner.com/brms/articles/brms_nonlinear.html)
4. [Andrew Proctor's - Module 6](https://andrewproctor.github.io/rcourse/module6.html)
5. [van de Schoot et al., 2021](https://www.nature.com/articles/s43586-020-00001-2)

### Priors 

Bayesian analyses rely on supplying uninformed or informed prior distributions 
for each parameter (coefficient; predictor) in the model. The default informed
priors for a one source model are the following, $\Delta N$ assumes a normal 
distribution (`dn`; $\mu = 3.4$; 
$\sigma = 0.25$), trophic position assumes a uniform distribution 
(lower bound = 2 and upper bound = 10), $\sigma$ assumes a uniform 
distribution (lower bound = 0 and upper bound = 10) and if 
informed priors are desired for $\delta^{15}N_b$ (`n1`; $\mu = 9$; 
$\sigma = 1$), we can set the argument `bp` to `TRUE` in 
all `one_source_` functions. 

You can change these default priors using 
`one_source_priors_params()`, however, I would suggest becoming familiar with 
Bayesian analyses, your study species, and system prior to adjusting these values. 

### Model convergence 

Some important things to pay attention to are 
always run at least 2 chains, if the model does not converge you can try 
to increase the following: 

1. The amount of samples that are burned-in (discarded; in `brm()` 
this can be controlled by the argument `warmup`)

2. The number of iterative samples retained (in `brm()` this can be controlled 
by the argument `iter`). 

3. The number of samples drawn (in `brm()` this is controlled by the argument 
`thin`).

4. Adjust the `adapt_delta` value using `control = list(adapt_delta = 0.95)`. 

When assessing the model we want R-hat to be 1 or within 0.05 of 1, 
which indicates that the variance among and within chains is equal 
(See 
[{rstan} docmentation on R-hat](https://mc-stan.org/rstan/reference/Rhat.html)),
a high value for effective sample size (ESS), trace plots to look 
"grassy" or "caterpillar like", and posterior distributions to look relatively
normal. 

## Estimating trophic position 

We will use functions from [{trps}](https://benjaminhlina.github.io/trps/)
that drop into a [{brms}](https://paulbuerkner.com/brms/) model. These 
functions are `one_source_model()` which provides `brm()` the formula structure
needed to run a one source model. Next `brm()` needs the structure of the 
priors which is supplied to the `prior` argument using `one_source_priors()`. 
Lastly, values for these priors are supplied through the `stanvars` argument 
using `one_source_priors_params()`. You can adjust the mean ($\mu$), 
variance ($\sigma$), or upper and lower bounds (`lb` and `ub`) for each prior 
of the model using `one_source_priors_params()`, however, only adjust priors 
if you have a good grasp of Bayesian frameworks and your study system and 
species. 

### Model 
Let's run the model! 

```{r}
m <- brm(
  formula = one_source_model(),
  prior = one_source_priors(),
  stanvars = one_source_priors_params(),
  data = combined_iso_os,
  family = gaussian(),
  chains = 2,
  iter = 4000,
  warmup = 1000,
  cores = 4,
  seed = 4,
  control = list(adapt_delta = 0.95)
)
```

### Model output 

Let's view the summary of the model. 

```{r}
m
```
We can see that the R-hat is 1 meaning that variance among and within chains is 
equal (See 
[{rstan} docmentation on R-hat](https://mc-stan.org/rstan/reference/Rhat.html))
and that ESS is quite large. Overall, this means the model is converging 
and fitting accordingly. 

### Trace plots 
Let's view trace plots and posterior distributions for the model. 

```{r}
plot(m)
```

We can see that the trace plots look "grassy" meaning the model is converging! 

## Posterior draws 

Let's again look at the summary output from the model. 

```{r}
m
```

We can see that $\Delta N$ is estimated to be `3.37` with `l-95% CI` of `2.89`, 
and `u-95% CI` of `3.86`. If we move down to trophic position (`tp`) we 
see trophic position is estimated to be `4.54` with `l-95% CI` of `4.21`, 
and `u-95% CI` of `4.96`. 

### Extract posterior draws 

We will use functions from [{tidybayes}](http://mjskay.github.io/tidybayes/) to do this work. First we will look at 
the the names of the variables we want to extract using `get_variables()`. 

```{r}
get_variables(m)
```

You will notice that `"b_tp_Intercept"` is the name of the variable  
that we are wanting to extract. We then will extract
posterior draws using `gather_draws()`. We going to rename `"b_tp_Intercept"` 
to `tp`. 

```{r}
post_draws <- m %>% 
  gather_draws(b_tp_Intercept) %>% 
  mutate(
    ecoregion = "Embayment",
    common_name = "Lake Trout",
    .variable = "tp"
  ) %>% 
  dplyr::select(common_name, ecoregion, .chain:.value)
```

Let's view the `post_draws`

```{r}
post_draws
```
We can see that this consists of seven variables:
1. `ecoregion`,
2. `common_name`, 
3. `.chain`,
4. `.iteration`(number sampled after burn-in), 
5. `.draw` (number sampled from `iter`; adjusted using `thin`), 
6. `.variable` (this will have different variables depending on what is 
supplied to `gather_draws()`), 
7. `.value` (estimated value). 

## Extracting credible intervals 

Considering we are likely using this information for a paper or presentation, 
it is nice to be able to report the median and credible intervals (e.g., 
equal-tailed intervals; ETI). We can extract and export these values using 
`spread_draws()` and `median_qi` from 
[{tidybayes}](http://mjskay.github.io/tidybayes/). 

I have renamed `b_tp_Intercept` to `tp`, added the grouping columns, rounded 
all columns that are numeric to two decimal points using `mutate_if()` and 
rearranged the order of the columns using `dplyr::select()`. 

```{r, message=FALSE}
medians_ci <- m %>%
        spread_draws(b_tp_Intercept) %>%
        median_qi() %>% 
        rename(
          tp = b_tp_Intercept
        ) %>% 
  mutate(
    ecoregion = "Embayment", 
    common_name = "Lake Trout"
  ) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  dplyr::select(ecoregion, common_name, tp:.interval)
```

Let's view the output. 

```{r}
medians_ci
```

I like to use [{openxlsx}](https://ycphs.github.io/openxlsx/index.html) 
to export these values into a table that I can use for presentations and papers.
For the vignette I am not going to demonstrate how to do this but please 
check out `{openxlsx}`. 



## Ploting posterior distributions 

Now that we have our posterior draws extracted we can plot them. For comparing 
trophic position among species or groups, I like using either 
violin plots, interval points, or slab plots for posteriors. We can access 
violins through [{ggplot2}](https://ggplot2.tidyverse.org/) with the later being available in [{ggdist}](https://mjskay.github.io/ggdist/). 

### Density plot
For this example we first are going to plot the density for posterior
draws using `geom_density()`.

```{r}
ggplot(data = post_draws, aes(x = .value)) + 
  geom_density() + 
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank()
  ) + 
  labs(
    x = "P(Trophic Position | X)", 
    y = "Density"
  )
```

### Point interval

Next as a point interval plot using 
`stat_pointinterval()`. 
```{r}
ggplot(data = post_draws, aes(y = .value, 
                              x = common_name)) + 
  stat_pointinterval() + 
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank()
  ) + 
  labs(
    x = "P(Trophic Position | X)", 
    y = "Density"
  )
```

Congratulations we have estimate trophic position for Lake Trout! 

I'll demonstrate below how to run the model with an iterative process to 
produce estimates of trophic position for more than one group 
(e.g., comparing trophic position among species or in this 
case different ecoergion). 

## Working with multiple groups 

In [{trps}](https://benjaminhlina.github.io/trps/) we have a data set that has 
consumer and baseline data already joined 
for two ecoregions (`combined_iso`) using the same methods above. 
Let's look at this data frame. 

### Organize data - multiple groups 
```{r}
combined_iso
```

We can see that this data frame has isotope data for a 
second baseline (dreissenids; `d13c_b2` and `d15n_b2`) as well as the mean 
values for both baselines (`c1`-`n2`). These columns for the second baseline
are useful when estimating trophic position using a two source model but 
we do not need them for this analysis and they can be removed.

We can also confirm that this data set has one species, lake trout. 
```{r}
unique(combined_iso$common_name)
```

collected from two ecoregions in Lake Ontario. 

```{r}
unique(combined_iso$ecoregion)
```

Let's remove the columns we don't need, `d13c_b2`, `d15n_b2`, `c1`, `c2`, `n2`. 
We also need to add $\lambda$ to the data frame (`l1`). 
We are going to make a `name` column that will be the two groups we have 
`common_name` and `ecoregion` pasted together. We are doing this to make the 
iterative processes easier. 

```{r}
combined_iso_update <- combined_iso %>% 
  dplyr::select(-c(d13c_b1, d15n_b1, d13c_b2, d15n_b2, c1, c2, n2)) %>% 
  mutate(
    l1 = 2, 
    name = paste(ecoregion, common_name, sep = "_")
  ) %>% 
  dplyr::select(id, common_name, ecoregion, name, d13c:l1)

combined_iso_update
```

This example data is now ready to be analyzed. 

## Estimate trophic position - multiple groups 

We will use similar structure as before to model trophic position, 
however, we will first `split()` the data into a list for all groups 
and then use `map()` from [{purrr}](https://purrr.tidyverse.org/) 
to run the model for each group.

You will notice that the `brm()` call is exactly the same as when we ran the model
for one group. The only difference here is when using `map()`, the 
`data` argument in `brm()` needs to be replaced with `.x` to tell `brm()` where 
to get the data.

### Model - multiple groups 
Let's run the model! 

```{r}
m1 <- combined_iso_update %>% 
  split(.$name) %>% 
  map( ~ brm(
    formula = one_source_model(),
    prior = one_source_priors(),
    stanvars = one_source_priors_params(),
    data = .x,
    family = gaussian(),
    chains = 2,
    iter = 4000,
    warmup = 1000,
    cores = 4,
    seed = 4,
    control = list(adapt_delta = 0.95)
  ), 
  .progress = TRUE
  )
```

### Model output - multiple groups 
Let's look at the summary of both models. 

```{r}
m1
```

We can see that the R-hat is 1, meaning that the variance among and within chains is 
equal (See [{rstan} docmentation on R-hat](https://mc-stan.org/rstan/reference/Rhat.html))
and that ESS is quite large for both groups. 
Overall, this means the both models are converging and fitting accordingly. 

### Trace plots - multiple groups 

Let's look at the trace plots and distributions. We will use `iwalk()` instead 
of `map()` here as `iwalk()` invisibly return `.x` which is handy when you want 
to call a function (e.g., `plot()`) for its side effects rather than its 
returned value.
I have also added `grid.text()` from {grid} to add the group names to each plot. 

```{r}

m1 %>% 
  iwalk(~ {
    plot(.x) 
    grid.text(.y, x = 0.5, y = 0.98)
  })
```

We can see that the trace plots look "grassy" meaning the model is converging! 

## Posterior draws - multiple groups 

Let's again look at the summary output from the model. 

```{r}
m1
```

We can see for lake trout from the `Anthropogenic` ecoregion that
$\Delta N$ is estimated to be `3.38` with `l-95% CI` of `2.88`, 
and `u-95% CI` of `3.87`. If we move down to trophic position (`tp`) we 
see trophic position is estimated to be `4.42` with `l-95% CI` of `4.44`, 
and `u-95% CI` of `5.29`. 

We can see for lake trout from the `Embayment` ecoregion that 
$\Delta N$ is estimated to be `3.37` with `l-95% CI` of `2.89`, 
and `u-95% CI` of `3.86`. If we move down to trophic position (`tp`) we 
see trophic position is estimated to be `4.54` with `l-95% CI` of `4.21`, 
and `u-95% CI` of `4.96`. 

### Extract posterior draws - multiple groups 

We will use functions from [{tidybayes}](http://mjskay.github.io/tidybayes/) 
to do this work. First we will look at 
the the names of the variables we want to extract using `get_variables()`. 
Considering we have multiple models in `m1` that have all of the same 
structure we can just look at the names of the first model object in `m1`. 

```{r}
get_variables(m1[[1]])
```

You will notice that `"b_tp_Intercept"` is the name of the variable  
that we are wanting to extract. We then will extract
posterior draws using `gather_draws()`. We going to rename `"b_tp_Intercept"` 
to `tp`. 

Again, considering we have multiple models in `m1` we need to use `map()` 
to iterate over `m1` to get the posterior draws. Once we have iterated over 
`m1` to extract draws we can combine the results using `bind_rows()` from 
[{dplyr}](https://dplyr.tidyverse.org/). The variable `name` will have the 
name of the ecoregion and common name of the species, however, they will 
pasted to together by a `_`. We need separate this string into the two 
variables we want `ecoregion` and `common_name`. We can do this by using
`separate_wider_delim()` from [{tidyr}](https://tidyr.tidyverse.org/). 
When using this function it will separate the columns and 
keep them as `characters`, hence why the last step is to convert `ecoregion` 
into a `factor`. 

For your data you will likley have other catogory names than `ecoregion` 
and `common_name`. Please replace with the columns that fit your data structure.

```{r}
post_draws_mg <- m1 %>%
  map(~ .x %>% 
        gather_draws(b_tp_Intercept) %>% 
        mutate(
          .variable = "tp"
        ) %>% 
        ungroup()
  ) %>% 
  bind_rows(.id = "name") %>% 
  separate_wider_delim(name, names = c("ecoregion", "common_name"), 
                       delim = "_", cols_remove = FALSE) %>% 
  mutate(
    ecoregion = factor(ecoregion, 
                       levels = c("Anthropogenic", "Embayment")), 
  )
```

Let's view the `post_draws_mg`

```{r}
post_draws_mg
```

1. `ecoregion`,
2. `common_name`, 
3. `.chain`,
4. `.iteration`(number sampled after burn-in), 
5. `.draw` (number sampled from `iter`; adjusted using `thin`), 
6. `.variable` (this will have different variables depending on what is 
supplied to `gather_draws()`), 
7. `.value` (estimated value). 

Note - the names of and items in the first two columns will vary 
depending on the names you split your data into. 

## Extracting credible intervals - multiple groups 

Considering we are likely using this information for a paper or presentation, 
it is nice to be able to report the median and credible intervals (e.g., 
equal-tailed intervals; ETI). We can extract and export these values using 
`spread_draws()` and `median_qi` from 
[{tidybayes}](http://mjskay.github.io/tidybayes/). 

Again, `m1` is a `list`of our model objects, we need to `map()` over 
the list to calculate these. Then we will do the same procedures we have done 
before in combining our outputs and get the names of each group correct. 
Lastly, we will use `mutate_if()` to round all columns that are 
numeric to two decimal points. 

```{r, message=FALSE}
post_medians_ci <- m1 %>%
  map(~ .x %>% 
        spread_draws(b_tp_Intercept) %>%
        median_qi() %>% 
        rename(
          tp = b_tp_Intercept
        ) 
  ) %>% 
  bind_rows(.id = "name") %>% 
  separate_wider_delim(name, names = c("ecoregion", "common_name"), 
                       delim = "_", cols_remove = FALSE) %>% 
  mutate(
    ecoregion = factor(ecoregion, 
                       levels = c("Anthropogenic", "Embayment")), 
  ) %>% 
  mutate_if(is.numeric, round, digits = 2)
```

Let's view the output. 

```{r}
post_medians_ci
```

I like to use [{openxlsx}](https://ycphs.github.io/openxlsx/index.html) 
to export these values into a table that I can use for presentations and papers.
For the vignette I am not going to demonstrate how to do this but please 
check out `{openxlsx}`. 

## Ploting posterior distributions - multiple groups 

Now that we have our posterior draws extracted we can plot them. For comparing 
trophic position among species or groups, I like using either 
violin plots, interval points, or slab plots for posteriors. We can access 
violins through [{ggplot2}](https://ggplot2.tidyverse.org/) with the later 
being available in [{ggdist}](https://mjskay.github.io/ggdist/). 

### Violin plot
Let's first look at the violin plot. 
```{r}
ggplot(data = post_draws_mg, aes(x = common_name, 
                                 y = .value, 
                                 fill = ecoregion)) + 
  geom_violin() + 
  stat_summary(fun = median, geom = "point", 
               size = 3, 
               position = position_dodge(0.9)
  ) + 
  scale_fill_viridis_d(name = "Ecoregion", 
                       option = "G", 
                       begin = 0.35, 
                       end = 0.75, alpha = 0.65) + 
  theme_bw(base_size = 15) + 
  theme(
    panel.grid = element_blank(),
    legend.position = "inside", 
    legend.position.inside = c(0.85, 0.86)
  ) +
  labs(
    x = "Species", 
    y = "P(Trophic Position | X)"
  )
```

### Point interval plot 

Next, let's look at the point interval plot but first we need to create our 
colour palette. 

```{r}
viridis_colours <- viridis(2,
                           option = "G",
                           begin = 0.35, 
                           end = 0.75, 
                           alpha = 0.65)
```

Now let's plot the point intervals. 

```{r}
ggplot(data = post_draws_mg, aes(x = common_name, 
                                 y = .value, 
                                 group = ecoregion)) + 
  stat_pointinterval(
    aes(point_fill = ecoregion),
    point_size = 4,
    interval_colour = "grey60",
    position = position_dodge(0.4),
    shape = 21,
  ) + 
  scale_fill_manual(aesthetics = "point_fill",
                    values = viridis_colours,
                    name = "Ecoregion") +
  theme_bw(base_size = 15) + 
  theme(
    panel.grid = element_blank(),
    legend.position = "inside", 
    legend.position.inside = c(0.85, 0.86)
  ) +
  labs(
    x = "Species", 
    y = "P(Trophic Position | X)"
  )
```


Congratulations we have successfully run a Bayesian one source trophic position 
model for one species in two ecoregions of Lake Ontario! 
