---
title: "Estimate trophic position - one source model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate trophic position - one source model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Our Objectives
The purpose of this vignette is to learn how to estimate trophic position of a 
species using stable isotope data
($\delta^{13}C$ and $\delta^{15}N$). We can estiamte trophic psoition using 
a one source model based on equations from 
[Post 2002](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2).

## Trophic Position Model
For a one source model from [Post 2002](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2)
the equation consists of the following: 


$$
\text{Trophic Position} = \lambda + \frac{(\delta^{15}N_c - \delta^{15}N_b)}{\Delta N}
$$


Where $\lambda$ is the trophic position of the baseline (e.g., `2`), 
$\delta^{15}N_c$ is the $\delta^{15}N$ of the consumer, $\delta^{15}N_b$ is the 
$\delta^{15}N$ of the baseline, and $\Delta N$ is the trophic enrichment factor 
(e.g., 3.4). 

To estimate trophic position using a Bayesian framework we need to rearrange 
this equation to the following: 


$$
\delta^{15}N_c = \delta^{15}N_b + \Delta N \times (\text{Trophic Position} - \lambda)  
$$


Functions in {trps} use this rearranged equation to estimate trophic position. 

## Vignette structure   
First we will need to do a bit of organizing the data prior to running the model. 
To do this work we will use [{dplyr}](https://dplyr.tidyverse.org/) and 
[{tidyr}]() but we could also use 
[{data.table}](https://rdatatable.gitlab.io/data.table/) to do this work. 

When running the model we will use [{trps}](https://benjaminhlina.github.io/trps/) 
and [{brms}](https://paulbuerkner.com/brms/) and iterative processes provided 
by [{purrr}](https://purrr.tidyverse.org/). 

Once we have run the model we will use [{bayesplot}](https://mc-stan.org/bayesplot/) 
to assess models and then extract posterior draws using 
[{bayestestR}](https://easystats.github.io/bayestestR/) and 
[{tidybayes}](http://mjskay.github.io/tidybayes/). 
Posterior distributions will be plotted using [{ggplot2}](https://ggplot2.tidyverse.org/) 
and [{ggdist}](https://mjskay.github.io/ggdist/).

## Load packages 
```{r setup, message=FALSE}
{
  library(bayesplot)
  library(bayestestR)
  library(brms)
  library(dplyr)
  library(ggplot2)
  library(ggdist)
  library(purrr)
  library(tidybayes)
  library(trps)
}
```

## Assess data 

In [{trps}]() we have several data sets, they include stable isotope data
($\delta$<sup>13</sup>C and $\delta$<sup>15</sup>N) for a
consumer, lake trout (*Salvelinus namaycush*), a benthic baseline, amphipods, 
and a pelagic baseline, dreissenids for two ecoregions in Lake Ontario. 

### Consumer data
We will check out each data set with the first being the consumer. 
```{r}
consumer_iso
```

We can see that this data set contains the common name of the consumer 
(`common_name`), the ecoregion samples were collected (`ecoregion`) and 
$\delta$<sup>13</sup>C (`d13c`) and $\delta$<sup>15</sup>N (`d15n`). 

### Baseline data 
Next for this vignette we will only assess benthic baseline data set 

```{r}
baseline_1_iso
```

We can see that this data set contains the common name of the baseline 
(`common_name`), the ecoregion samples were collected (`ecoregion`) and 
$\delta$<sup>13</sup>C (`c1`) and $\delta$<sup>15</sup>N (`n1`). 

## Organizing data 

Now that we understand the data we need to combine the data to estimate 
trophic position for our consumer. To do this we first need to make an `id` 
column in each data set that will assist in joining data. 

### Consumer data

Let us first do this to the `consumer_iso` data frame.  
 
```{r}
consumer_iso <- consumer_iso %>% 
  group_by(common_name, ecoregion) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, common_name:d15n)
```

### Baseline data 

Next let us do this to the `baseline_1_iso` data frame. For joining purposes we 
are going to drop `common_name` from this data frame. 

```{r}
baseline_1_iso <- baseline_1_iso %>% 
  group_by(common_name, ecoregion) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, ecoregion:n1)
```

### Joining isotope data 
Now that we have both the consumer and baseline data frames having consistent
structure we can join them to then use in the analysis. We will also add in 
a constant $\lambda$ (`l1`) to our data frame. 

```{r}
combined_iso_os <- consumer_iso %>% 
  left_join(baseline_1_iso, by = c("id", "ecoregion")) %>% 
  mutate(
    l1 = 2
  )
```

We can see that this has successfully combined our consumer and baseline data. 
```{r}
combined_iso_os
```

## Bayesian Analysis

We can now estimate trophic position for lake trout in an ecoregion of
Lake Ontario. 

There are a few things to know about running a Bayesian analysis, I suggest 
reading a these resources. 

Bayesian analyses rely on supplying uninformed or informed prior distributions 
for each parameter (coefficient; predictor) in the model.

Some important things to pay attention to are 
always run at least 2 chains, if the model does not converge you can try 
to adjust the amount of samples that are burned-in (discarded; in brms 
this can be controlled by the argument `warmup`), adjust the number of 
iterative samples retained (in brms this can be controlled by the 
argument `iter`), and/or adjust the `adapt_delta` value using 
`control = list(adapt_delta = 0.95)`. 

When assessing the model we want rhat to be 1 or within 0.05 of 1, we also want 
a high value for effective sample size (ESS), we want trace plots to look 
"grassy" or "catapillery", and we want posterior distributions to look relatively
normal. 

## Estimating trophic position 

We will use functions from {trps} that drop into a {brms} model. These 
functions are `one_source_model()` which provides `brm()` the formula structure
needed to run a one source model. Next is `brm()` needs the structure of the 
priors which can be supplied to the `prior` argument using `one_source_priors()`. 
Lastly, values for these priors are supplied through the `stanvars` argument 
using `one_source_priors_params()`. You can adjust the mean ($\mu$),  
variance ($\sigma$), or upper and lower bounds (`lb` and `ub`) for each prior 
of the model within `one_soruce_priors_params()`, however, only adjust priors 
if you have a good grasp of Bayesian frameworks and your study system and 
species. 

```{r}
m <- brm(
  formula = one_source_model(),
  prior = one_source_priors(),
  stanvars = one_source_priors_params(),
  data = combined_iso_os,
  family = gaussian(),
  chains = 2,
  iter = 4000,
  warmup = 1000,
  cores = 4,
  seed = 4,
  control = list(adapt_delta = 0.95)
)
```

Let us view a summary of the model  

```{r}
m
```

Let us view trace plots and posterior distributions 

```{r}
plot(m)
```

