---
title: "Getting started with trps"
author: Benjamin L. Hlina
date: "2025-02-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with trps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

## Our Objectives

The purpose of this vignette is to learn how to estimate trophic position 
of a species using stable isotope data ($\delta^{13}C$ and $\delta^{15}N$). 
We can estimate trophic position using several different models but for the purpose 
of getting started a one source model is the simplist and easiest to implement. 
The one source model is based on equations from [Post (2002)](ttps://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/0012-9658%282002%29083%5B0703%3AUSITET%5D2.0.CO%3B2).

We are starting out with the simplest model. If you are wanting to use other 
trophic position models please walk through this vignette and then
check out those vignettes under the article section of the webpage. 

## Trophic Position Model

The equation for a one source model consists of the following:

$$
\text{Trophic Position} = \lambda + \frac{(\delta^{15}N_c - \delta^{15}N_b)}{\Delta N}
$$

Where $\lambda$ is the trophic position of the baseline (e.g., `2`), $\delta^{15}N_c$ is the $\delta^{15}N$ of the consumer, $\delta^{15}N_b$ is the mean $\delta^{15}N$ of the baseline, and $\Delta N$ is the trophic enrichment factor (e.g., 3.4).

To use this model with a Bayesian framework, we need to rearrange this equation to the following:

$$
\delta^{15}N_c = \delta^{15}N_b + \Delta N \times (\text{Trophic Position} - \lambda) 
$$

The function `one_source_model()` uses this rearranged equation.

## Vignette structure

First we need to organize the data prior to running the model. To do this work we will use [{dplyr}](https://dplyr.tidyverse.org/) and [{tidyr}](https://tidyr.tidyverse.org/) but we could also use [{data.table}](https://rdatatable.gitlab.io/data.table/).

When running the model we will use [{trps}](https://benjaminhlina.github.io/trps/) and [{brms}](https://paulbuerkner.com/brms/). 

Once we have run the model we will use [{bayesplot}](https://mc-stan.org/bayesplot/) to assess models and then extract posterior draws using [{tidybayes}](http://mjskay.github.io/tidybayes/). Posterior distributions will be plotted using [{ggplot2}](https://ggplot2.tidyverse.org/) and [{ggdist}](https://mjskay.github.io/ggdist/) with colours provided by [{viridis}](https://sjmgarnier.github.io/viridis/).

## Load packages

First we load all the packages needed to carry out the analysis.

```{r setup, message=FALSE}
{
library(bayesplot)
library(brms)
library(dplyr)
library(ggplot2)
library(ggdist)
library(grid)
library(tidybayes)
library(tidyr)
library(trps)
library(viridis)
}
```

## Assess data

In [{trps}](https://benjaminhlina.github.io/trps/) we have several data sets, they include stable isotope data ($\delta^{13}C$ and $\delta^{15}N$) for a consumer, lake trout (*Salvelinus namaycush*), a benthic baseline, amphipods, and a pelagic baseline, dreissenids, for an ecoregion in Lake Ontario.

### Consumer data

We check out each data set with the first being the consumer.

```{r}
consumer_iso
```

We can see that this data set contains the `common_name` of the consumer , the `ecoregion` samples were collected from, and $\delta^{13}C$ (`d13c`) and $\delta^{15}N$ (`d15n`).

### Baseline data

Next we check out the benthic baseline data set.

```{r}
baseline_1_iso
```

We can see that this data set contains the `common_name` of the baseline, the `ecoregion` samples were collected from, and $\delta^{13}C$ (`d13c_b1`) and $\delta^{15}N$ (`d15n_b1`).

## Organizing data

Now that we understand the data we need to combine both data sets to estimate trophic position for our consumer.

To do this we first need to make an `id` column in each data set, which will allow us to join them together. We first `arrange()` the data by `ecoregion` and `common_name`. Next we `group_by()` the same variables, and add `id` for each grouping using `row_number()`. Always `ungroup()` the `data.frame` after using `group_by()`. Lastly, we use `dplyr::select()` to rearrange the order of the columns.

### Consumer data

Let's first add `id` to `consumer_iso` data frame.

```{r}
con_os <- consumer_iso %>% 
  arrange(ecoregion, common_name) %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, common_name:d15n)
```


You will notice that I have renamed this object to `con_os` this is 
because we are modifying `con_os`. I have done the same to the baseline and 
combined objects below. 

### Baseline data

Next let's add `id` to `baseline_1_iso` data frame. For joining purposes we are going to drop `common_name` from this data frame.

```{r}
b1_os <- baseline_1_iso %>% 
  arrange(ecoregion, common_name) %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    id = row_number()
  ) %>% 
  ungroup() %>% 
  dplyr::select(id, ecoregion:d15n_b1)
```

### Joining isotope data

Now that we have the consumer and baseline data sets in a consistent format we can join them by `"id"` and `"ecoregion"` using `left_join()` from [{dplyr}](https://dplyr.tidyverse.org/).

```{r}
combined_iso_os <- con_os %>% 
  left_join(b1_os, by = c("id", "ecoregion"))
```

We can see that we have successfully combined our consumer and baseline data. We need to do one last thing prior to analyzing the data, and that is calculate the mean $\delta^{13}C$ (`c1`) and $\delta^{15}N$ (`n1`) for the baseline and add in the constant $\lambda$ (`l1`) to our data frame. We do this by using `groub_by()` to group the data by our two groups, then using `mutate()` and `mean()` to calculate the mean values.

Important note, to run the model successfully, columns need to be named `d15n`, `n1`, and `l1`.

```{r}
combined_iso_os_1 <- combined_iso_os %>% 
  group_by(ecoregion, common_name) %>% 
  mutate(
    c1 = mean(d13c_b1, na.rm = TRUE),
    n1 = mean(d15n_b1, na.rm = TRUE),
    l1 = 2
  ) %>% 
  ungroup()
```

Let's view our combined data.

```{r}
combined_iso_os_1
```

It is now ready to be analyzed!

## Bayesian Analysis

We can now estimate trophic position for lake trout in an ecoregion of Lake Ontario.

There are a few things to know about running a Bayesian analysis, I suggest reading these resources:

1.  [Basics of Bayesian Statistics - Book](https://statswithr.github.io/book/)
2.  [General Introduction to brms](https://www.jstatsoft.org/article/view/v080i01)
3.  [Estimating non-linear models with brms](https://paulbuerkner.com/brms/articles/brms_nonlinear.html)
4.  [Nonlinear modelling using nls nlme and brms](https://www.granvillematheson.com/post/nonlinear-modelling-using-nls-nlme-and-brms/)
5.  [Andrew Proctor's - Module 6](https://andrewproctor.github.io/rcourse/module6.html)
6.  [van de Schoot et al., (2021)](https://www.nature.com/articles/s43586-020-00001-2)

### Priors

Bayesian analyses rely on supplying uninformed or informed prior distributions for each parameter (coefficient; predictor) in the model. The default informed priors for a one source model are the following, $\Delta N$ assumes a normal distribution (`dn`; $\mu = 3.4$; $\sigma = 0.25$), trophic position assumes a uniform distribution (lower bound = 2 and upper bound = 10), $\sigma$ assumes a uniform distribution (lower bound = 0 and upper bound = 10), and if informed priors are desired for $\delta^{15}N_b$ (`n1`; $\mu = 9$; $\sigma = 1$), we can set the argument `bp` to `TRUE` in all `one_source_` functions.

You can change these default priors using `one_source_priors_params()`, however, I would suggest becoming familiar with Bayesian analyses, your study species, and system prior to adjusting these values.

### Model convergence

It is important to always run the model with at least 2 chains. If the model does not converge you can try to increase the following:

1.  The amount of samples that are burned-in (discarded; in `brm()` this can be controlled by the argument `warmup`)

2.  The number of iterative samples retained (in `brm()` this can be controlled by the argument `iter`).

3.  The number of samples drawn (in `brm()` this is controlled by the argument `thin`).

4.  The `adapt_delta` value using `control = list(adapt_delta = 0.95)`.

When assessing the model we want $\hat R$ to be 1 or within 0.05 of 1, which indicates that the variance among and within chains are equal (see [{rstan} documentation on $\hat R$](https://mc-stan.org/rstan/reference/Rhat.html)), a high value for effective sample size (ESS), trace plots to look "grassy" or "caterpillar like," and posterior distributions to look relatively normal.

## Estimating trophic position

We will use functions from [{trps}](https://benjaminhlina.github.io/trps/) that drop into a [{brms}](https://paulbuerkner.com/brms/) model. These functions are `one_source_model()` which provides `brm()` the formula structure needed to run a one source model. Next `brm()` needs the structure of the priors which is supplied to the `prior` argument using `one_source_priors()`. Lastly, values for these priors are supplied through the `stanvars` argument using `one_source_priors_params()`. You can adjust the mean ($\mu$), variance ($\sigma$), or upper and lower bounds (`lb` and `ub`) for each prior of the model using `one_source_priors_params()`, however, only adjust priors if you have a good grasp of Bayesian frameworks and your study system and species.

### Model

Let's run the model!

```{r}
m <- brm(
  formula = one_source_model(),
  prior = one_source_priors(),
  stanvars = one_source_priors_params(),
  data = combined_iso_os_1,
  family = gaussian(),
  chains = 2,
  iter = 4000,
  warmup = 1000,
  cores = 4,
  seed = 4,
  control = list(adapt_delta = 0.95)
)
```

### Model output

Let's view the summary of the model.

```{r}
m
```

We can see that $\hat R$ is 1 meaning that variance among and within chains are equal (see [{rstan} documentation on $\hat R$](https://mc-stan.org/rstan/reference/Rhat.html)) and that ESS is quite large. Overall, this means the model is converging and fitting accordingly.

### Trace plots

Let's view trace plots and posterior distributions for the model.

```{r}
plot(m)
```

We can see that the trace plots look "grassy" meaning the model is converging!

## Predictive posterior check 

We can check how well the model is predicting the $\delta^{15}N$ of the consumer
using `pp_check()` from `{bayesplot}`. 

```{r}
pp_check(m)
```

We can see that posteriors draws ($y_{rep}$; light lines) are effectively 
modeling $\delta^{15}N$ of the consumer ($y$; dark line). 

## Posterior draws

Let's again look at the summary output from the model.

```{r}
m
```

We can see that $\Delta N$ is estimated to be `3.37` with `l-95% CI` of `2.89`, 
and `u-95% CI` of `3.86`. If we move down to trophic position (`tp`) 
we see trophic position is estimated to be `4.54` 
with `l-95% CI` of `4.21`, and `u-95% CI` of `4.96`.

### Extract posterior draws

We use functions from [{tidybayes}](http://mjskay.github.io/tidybayes/) 
to do this work. First we look at the the names of the variables we want to extract using `get_variables()`.

```{r}
get_variables(m)
```

You will notice that `"b_tp_Intercept"` is the name of the variable that we are wanting to extract. We extract posterior draws using `gather_draws()`, and rename `"b_tp_Intercept"` to `tp`.

```{r}
post_draws <- m %>% 
  gather_draws(b_tp_Intercept) %>% 
  mutate(
    ecoregion = "Embayment",
    common_name = "Lake Trout",
    .variable = "tp"
  ) %>% 
  dplyr::select(common_name, ecoregion, .chain:.value)
```

Let's view the `post_draws`

```{r}
post_draws
```

We can see that this consists of seven variables:

1.  `ecoregion`
2.  `common_name`
3.  `.chain`
4.  `.iteration` (number of sample after burn-in)
5.  `.draw` (number of samples from `iter`)
6.  `.variable` (this will have different variables depending on what is supplied to `gather_draws()`)
7.  `.value` (estimated value)

## Extracting credible intervals

Considering we are likely using this information for a paper or presentation, it is nice to be able to report the median and credible intervals (e.g., equal-tailed intervals; ETI). We can extract and export these values using `spread_draws()` and `median_qi` from [{tidybayes}](http://mjskay.github.io/tidybayes/).

We rename `b_tp_Intercept` to `tp`, add the grouping columns, round all columns that are numeric to two decimal points using `mutate_if()`, and rearrange the order of the columns using `dplyr::select()`.

```{r, message=FALSE}
medians_ci <- m %>%
        spread_draws(b_tp_Intercept) %>%
        median_qi() %>% 
        rename(
          tp = b_tp_Intercept
        ) %>% 
  mutate(
    ecoregion = "Embayment", 
    common_name = "Lake Trout"
  ) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  dplyr::select(ecoregion, common_name, tp:.interval)
```

Let's view the output.

```{r}
medians_ci
```

I like to use [{openxlsx}](https://ycphs.github.io/openxlsx/index.html) to export these values into a table that I can use for presentations and papers. For the vignette I am not going to demonstrate how to do this but please check out `{openxlsx}`.

## Plotting posterior distributions – single species or group

Now that we have our posterior draws extracted we can plot them. To analyze *a single* species or group, I like using density plots.

### Density plot

For this example we first plot the density for posterior draws using `geom_density()`.

```{r}
ggplot(data = post_draws, aes(x = .value)) + 
  geom_density() + 
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank()
  ) + 
  labs(
    x = "P(Trophic Position | X)", 
    y = "Density"
  )
```

### Point interval

Next we plot it as a point interval plot using `stat_pointinterval()`.

```{r}
ggplot(data = post_draws, aes(y = .value, 
                              x = common_name)) + 
  stat_pointinterval() + 
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank()
  ) + 
  labs(
    x = "P(Trophic Position | X)", 
    y = "Density"
  )
```

Congratulations we have estimated the trophic position for Lake Trout!

I'll demonstrate in another vignette (i.e, [one source - multiple groups](estimate_trophic_position_one_source_multiple_groups.html)) how to run the model with an iterative process to produce estimates of trophic position for more than one group (e.g., comparing trophic position among species or in this case different ecoregions).

Now that you have gone through a one source model, you may be looking 
to model trophic position using a two source model. Please see the following 
vignette on how to setup and run a two source model 
[Estimate trophic position - two source model](estimate_trophic_position_two_source_model.html). 
The same iterative processes used in [one source - multiple groups](estimate_trophic_position_one_source_multiple_groups.html)
can be applied to the two sorce model. 
